Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-03 paper/paper.tex
pass

We evaluated \tname\ against \totalAttacks attacks of various kinds
(\eg{} Denial-of-Service (DoS)~\cite{denial-of-service}, Active
Reconnaissance (AREC)~\cite{active-reconnaissance} and Privilege
escalation (PESC)~\cite{privilege-escalation}) and from various
sources. Preliminary results provide early evidence that \tname\ is
promising. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top-1, top-3, top-5, and top-10 rules of
the ranking, respectively, in \percTopOneRanking\,
\percTopThreeRanking, \percTopFiveRanking, and \percTopTenRanking\ of
the cases.

@@

Overall, results show that \tname\ performed very well in most of the
cases. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top-1, top-3, top-5, and top-10 rules of
the ranking, respectively, in \percTopOneRanking\,
\percTopThreeRanking, \percTopFiveRanking, and \percTopTenRanking\ of
the cases.

@@

Network Intrusion Detectors are an important defense mechanism against
networks attacks. Generating rules to capture new attacks can be
time-consuming and error-prone. This paper presents \tname{}, a novel
approach to generate rules for Rule-based \nids. \tname\ leverages
positive and negative traffic and examples of trusted rules to
synthesize rules. \tname{} is organized as a pipeline of three
components that 1)~create an over-specified seed rule, 2)~derive
plausible rules from the seed, and 3)~rank plausible
rules. Experimental results provide early evidence showing that
\tname\ is promising. It was able to rank the correct rule among the
first ten rules of the reported ranking in \percTopFiveRanking\ of
the cases we analyzed, for example. The data set containing our
experimental artifacts is publicly accessible at \ourdataset.

>>>>

We evaluated \tname\ against \totalAttacks attacks of various kinds
(\eg{} Denial-of-Service (DoS)~\cite{denial-of-service}, Active
Reconnaissance (AREC)~\cite{active-reconnaissance} and Privilege
escalation (PESC)~\cite{privilege-escalation}) and from various
sources. Preliminary results provide early evidence that \tname\ is
promising. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top-1, top-3 and top-10 rules of
the ranking, respectively, in \percTopOneRanking\ ,
\percTopThreeRanking\ and \percTopTenRanking\ of
the cases.

@@

Overall, results show that \tname\ performed very well in most of the
cases. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top-1, top-3 and top-10 rules of
the ranking, respectively, in \percTopOneRanking\ ,
\percTopThreeRanking\ and \percTopTenRanking\ of
the cases.

@@

Network Intrusion Detectors are an important defense mechanism against
networks attacks. Generating rules to capture new attacks can be
time-consuming and error-prone. This paper presents \tname{}, a novel
approach to generate rules for Rule-based \nids. \tname\ leverages
positive and negative traffic and examples of trusted rules to
synthesize rules. \tname{} is organized as a pipeline of three
components that 1)~create an over-specified seed rule, 2)~derive
plausible rules from the seed, and 3)~rank plausible
rules. Experimental results provide early evidence showing that
\tname\ is promising. It was able to rank the correct rule among the
first ten rules of the reported ranking in \percTopTenRanking\ of
the cases we analyzed, for example. The data set containing our
experimental artifacts is publicly accessible at \ourdataset.
